The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-08-22 src/paper/theory.tex
Fix typo
Improve proof

Let us first establish the sum of the shares of all big players.
Then, the value of individual big players can be obtained by relying on the assumption of symmetry.
The following proposition provides an expression for the limit of this total value.
\begin{theorem}
    \label{prop:multiple_platforms_total}
    Let $f$ be continuous on [0, 1].
    Let us denote the number of fringe players in any coalition $S$ as $n_A(S)$.
    Furthermore, let us denote the random variable $\frac{n_A(\precede_{P_j})}{n}$ as $X_n^j$.
    Assume that $X_n^j$ and $X_n^k$ are independent for all $j \neq k$.
    Furthermore, supppose that $X_n^j \xrightarrow[]{d} X^j$ with cdf $G(t)$ and (if exists) pdf $g(t)$ for every $j = 1, \dots, m$.

@@

    For the fringe value, the proof is similar, with a couple of additional steps.
    First, fix some fringe player $A_{li}$.
    Let $Y_n$ be the random variable describing the share of each type of fringe player that precede player $A_{li}$.
    Also, let $Q_n$ be the random variable describing whether player $P$ precedes player $A_{li}$.
    Then, the value of fringe player $A_{li}$ is
    \begin{align*}
        \varphi_{A_{li}}^n &= \E[ \mathbf{1}[Q_n = 1] (f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)) ],
    \end{align*}
    and the value of the whole fringe of type $A_l$ is
    \begin{align*}
        \varphi_{A_{l}}^n = n \varphi_{A_{li}}^n = \E \bigg[ \underbrace{\mathbf{1}[Q_n = 1] \frac{f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)}{1/n}}_{\coloneqq \Delta_n} \bigg].
    \end{align*}

    Now notice that, because the number of fringe players goes to infinity,
    \begin{align*}
        X_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) &\implies Y_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) \\
        &\implies (Y_1, \dots, Y_n) | Y_l = a_l(s) \xrightarrow[]{d} (a_1(s), \dots, a_l(s)) .
    \end{align*}
    Furthermore,
    \begin{align*}
        \Pr(Q_n = 1 | [Y_n]_l = a_l(s)) \to H(s).
    \end{align*}
    Finally, for fixed $(Y_1, \dots, Y_L)$,
    \begin{align*}
        \Delta_n \to \partial_l f(Y_1, \dots, Y_l, \dots, Y_L).
    \end{align*}

    Putting it all together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_{A_{l}}^n &= \lim_{n \to \infty} \E[\Delta_n (Y_n)] \\
        &= \E[ H(s) \partial_l f(Y_1, \dots, Y_L) ] \\
        &= \int_0^1 H(s) \partial_l f(a_1(s), \dots, a_L(s)) \mathrm{d} a_l(s) \\
        &= \int_0^1 H(s) a_l'(s) \partial_l f(a_1(s), \dots, a_L(s)) \ds.
    \end{align*}

>>>>

Let us first establish the sum of the shares of all big players.
Then, the value of individual big players can be obtained by relying on the assumption of symmetry.
The following proposition provides an expression for the limit of this total value.
\begin{theorem}
    \label{prop:multiple_platforms_total}
    Let $f$ be continuous on [0, 1].
    Let us denote the number of fringe players in any coalition $S$ as $n_A(S)$.
    Furthermore, let us denote the random variable $\frac{n_A(\precede_{P_j})}{n}$ as $X_n^j$.
    Assume that $X_n^j$ and $X_n^k$ are independent for all $j \neq k$.
    Furthermore, suppose that $X_n^j \xrightarrow[]{d} X^j$ with cdf $G(t)$ and (if exists) pdf $g(t)$ for every $j = 1, \dots, m$.

@@

    For the fringe value, the proof is similar, with a couple of additional steps.
    First, fix some fringe player $A_{li}$.
    Let $Y_n = (Y_n^1, \dots, Y_n^L)$ be the random variable describing the share of each type of fringe player that precede player $A_{li}$.
    Also, let $Q_n$ be the random variable describing whether player $P$ precedes player $A_{li}$.
    Then, the value of fringe player $A_{li}$ is
    \begin{align*}
        \varphi_{A_{li}}^n &= \E[ \mathbf{1}[Q_n = 1] (f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)) ],
    \end{align*}
    and the value of the whole fringe of type $A_l$ is
    \begin{align*}
        \varphi_{A_{l}}^n = n \varphi_{A_{li}}^n &= \E \bigg[ \mathbf{1}[Q_n = 1] \underbrace{\frac{f(Y_n^1, \dots, Y_n^l + 1/n, \dots, Y_n^L) - f(Y_n^1, \dots, Y_n^l, \dots, Y_n^L)}{1/n}}_{\coloneqq \Delta_n} \bigg] \\
        &= \E_{Y_n^L} \Bigg[ \E \bigg[ \mathbf{1}[Q_n = 1] \underbrace{\frac{f(Y_n^1, \dots, Y_n^l + 1/n, \dots, Y_n^l) - f(Y_n^1, \dots, Y_n^l, \dots, Y_n^L)}{1/n}}_{\coloneqq \Delta_n} \bigg| Y_n^l \bigg] \Bigg].
    \end{align*}

    Now, notice that, because the number of fringe players goes to infinity,
    \begin{align*}
        X_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) &\implies Y_n \mid Y_n^l = y \xrightarrow[]{d} (a_1(a_l^{-1}(y)), \dots, a_L(a_l^{-1}(y))).
    \end{align*}
    Furthermore,
    \begin{align*}
        \Pr(Q_n = 1 | Y_n^l = y) \to H(a_l^{-1}(y)).
    \end{align*}
    Finally, for fixed $(Y_1, \dots, Y_L)$,
    \begin{align*}
        \Delta_n \to \partial_l f(Y_1, \dots, Y_l, \dots, Y_L).
    \end{align*}

    Putting it all together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_{A_{l}}^n &= \lim_{n \to \infty} \E[\mathbf{1}[Q_n = 1] \Delta_n (Y_n)] \\
        &= \E[ H(s) \partial_l f(Y_1, \dots, Y_L) ] \\
        &= \int_0^1 H(a_l^{-1}(y)) \partial_l f(a_1(a_l^{-1}(y)), \dots, a_L(a_l^{-1}(y))) \mathrm{d}y \\
        &= \int_0^1 H(s) a_l'(s) \partial_l f(a_1(s), \dots, a_L(s)) \ds.
    \end{align*}
